### 2017-06-26 paper/paper.tex
LaTeXed model

%%
%% Beginning of file 'sample61.tex'
%%
%% Modified 2016 September
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.1 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass{aastex61}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex61}
%% 
%% where the arguement options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex61}

%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\normal}{\ensuremath{{\rm N}}}

\newcommand{\nukl}{\ensuremath{\nu_{nk\ell}}}
\newcommand{\nukzero}{\ensuremath{\nu_{nk0}}}
\newcommand{\nukone}{\ensuremath{\nu_{nk1}}}
\newcommand{\nuzero}{\ensuremath{\nu_{n00}}}
\newcommand{\dnu}{\ensuremath{\Delta_\nu}}
\newcommand{\numax}{\ensuremath{\nu_{\rm max}}}
\newcommand{\numod}{\ensuremath{{\rm bell}}}
\newcommand{\amps}{\ensuremath{A_{nk\ell}}}
\newcommand{\ampc}{\ensuremath{B_{nk\ell}}}
\newcommand{\rl}{\ensuremath{r_{01}}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{July 1, 2016}
\revised{September 27, 2016}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{\aastex\ sample article}
\shortauthors{Feeney et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Asteroseismology {\it sans Fourier}: soon to be crushed by DFM}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.1 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.1 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Stephen M. Feeney}
\email{sfeeney@flatironinstitute.org}

\author[0000-0003-2268-2519]{Stephen M. Feeney}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

\author{David W. Hogg}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA }
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA }
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany }

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.1 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

Things, stuff.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices --- 
miscellaneous --- catalogs --- surveys}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

Consider a set of $2K+1$ modes, indexed by $k \in \mathbb{Z}: -K \le k \le K$. Assuming that the $\ell = 0, 1$ modes are present, we expect a comb of $4K+2$ peaks in the power spectrum. The $\ell = 0$ modes are located at
\begin{equation}
\nukzero = \nuzero (1 + k \dnu), 
\end{equation}
with the $\ell = 1$ modes shifted to
\begin{equation}
\nukone = \nuzero (1 + (k + 1/2) \dnu), 
\end{equation}
Each of these modes corresponds to two sinusoids
\begin{equation}
m(t) = \amps \sin(2\pi\nukl t) + \ampc \cos(2\pi\nukl t)
\end{equation}
into the stellar lightcurve. The amplitudes, $\{\amps, \ampc\}$, are normally distributed with a frequency- and $\ell$-dependent variance:
\begin{equation}
\amps, \ampc \sim \normal \left(\amps, \ampc; 0, \rl^\ell \sigma^2(\nukl) \right),
\end{equation}
where $\rl$, the ratio of the variances of the $\ell = 0$ and $\ell = 1$ modes with equal $k$, is approximately 1/2. The variance, $\sigma^2(\nukl)$, of the amplitudes is modulated by a bell-shaped envelope, yielding
\begin{equation}
\sigma^2(\nu) = \numod(\nu; \numax, W, H),
\end{equation}
where
\begin{equation}
\numod(\nu; \numax, W, H) = H \exp \left( -\frac{(\nu - \numax)^2}{2 W^2} \right).
\end{equation}

This model is completely described by the parameters $\{ \amps, \ampc, \nuzero, \dnu, \rl, \numax, W, H \}$, depending linearly on the amplitudes, $\{\amps, \ampc\}$, and non-linearly on the remainder. In the following, we assume $K=16$, yielding a total of 132 linear parameters and six non-linear parameters.

\end{document}

% End of file `sample61.tex'.

### 2017-06-30 paper/paper.tex

@@
 %% using aastex version 6.1
-\documentclass{aastex61}
+\documentclass[modern]{aastex61}
 
@@
 
-\author{David W. Hogg}
+\author[0000-0003-2866-9403]{David W. Hogg}
 \affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
-\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA }
+\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA }
 \affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA }
@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction}\label{sec:intro}
+
+Asteroseismology is performed by taking continuous, excellent data.
+
+Parameter estimation is done by looking at the FT of the time-domain data.
+
+The FT is much cleaner when the data is regularly spaced, close to
+homoskedastic, and taken identically.
+
+For example, the FT of the data is the multiply of the FT of the star
+with the FT of the exposure-time window, so the whole project breaks
+if the exposure time is varied.
+
+For another example, there is no traditional way to do
+asteroseismology with sparse-in-time data, like that which will be
+produced by LSST and Gaia.
+
+For yet another: Time-localized outlers are death in the Fourier domain.
+
+But in asteroseismology we are only trying to learn a very small number
+of scalars from the light curve. Do we really need to beat the light curve
+against every possible period?
+
+Finally: Stars are damned coherent. Red giants, in particular, show little
+or no sign of decoherence over the entire duration of the Kepler mission.
+That should make life better; how?
+
+Here we capitalize on the near-coherence of the modes over reasonable
+time periods (and the magic of Gaussians) to perform asteroseismic
+parameter estimation in the time domain, without any use of the
+Fourier transform.
+
+\section{Method}\label{sec:method}
 

### 2017-07-01 paper/paper.tex
move abstract from readme to paper

@@
 
+\newcommand{\acronym}[1]{{\small{#1}}}
+\newcommand{\project}[1]{\textsl{#1}}
+\newcommand{\kepler}{\project{Kepler}}
+\newcommand{\tess}{\project{\acronym{TESS}}}
+\newcommand{\gaia}{\project{Gaia}}
+\newcommand{\lsst}{\project{\acronym{LSST}}}
+
 \newcommand{\normal}{\ensuremath{{\rm N}}}
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{July 1, 2016}
-\revised{September 27, 2016}
-\accepted{\today}
+\received{TBD}
+\revised{NA}
+\accepted{NA}
 %% Command to document which AAS Journal the manuscript was submitted to.
@@
 \begin{abstract}
-
-Things, stuff.
-
+Stellar oscillations are stochastically driven high-*Q* modes.
+If a star is observed through an observing campaign that is shorter
+than the coherence time of a mode, that mode will effectively appear
+coherent within that time interval.
+Here we exploit this to create an inexpensive probabilistic model for
+asteroseismology data.
+The huge advantage of this approach to traditional asteroseismology
+approaches is that it does not require the performance of a fourier
+transform or anything like it; this permits the measurement of
+asteroseismic parameters in data sets that are irregularly or sparsely
+sampled, or in data sets where the critical modes are near the edges
+of the available frequency space (near the inverse exposure time at
+the high-frequency end or near the inverse of the duration of the
+campaign at the low-freqency end).
+It also permits the construction of a tractable and justifiable
+likelihood function, even when the noise processes are non-trivial.
+We produce a parameterized description of an asteroseismic frequency
+spectrum and use it along with this likelihood function to produce
+posterior estimates of asteroseismic parameters for stars in the
+\kepler\ data.
+We sub-sample the \kepler\ light curves to (short duration)
+\tess-like and (sparsely sampled) \gaia-like data sets and show that
+even in these much smaller data sets, we ought to be able to estimate
+asteroseismic parameters for many stars, and (because we are just
+turning the Bayesian crank) without human intervention.
 \end{abstract}
@@
 %% keywords and the rules for their use.
-\keywords{editorials, notices --- 
-miscellaneous --- catalogs --- surveys}
+\keywords{editorials, notices --- miscellaneous --- catalogs ---
+  surveys --- methods of limited utility}
 
@@
 asteroseismology with sparse-in-time data, like that which will be
-produced by LSST and Gaia.
+produced by \lsst\ and \gaia.
 
@@
 Finally: Stars are damned coherent. Red giants, in particular, show little
-or no sign of decoherence over the entire duration of the Kepler mission.
+or no sign of decoherence over the entire duration of the \kepler\ Mission.
 That should make life better; how?

### 2017-07-01 paper/paper.tex
abstract work

@@
 \newcommand{\lsst}{\project{\acronym{LSST}}}
+\newcommand{\bsa}{\project{\acronym{BSA}}}
 
@@
 
-\begin{document}
+\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust the Hogg
 
@@
 %% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-Stellar oscillations are stochastically driven high-*Q* modes.
+\begin{abstract}\noindent % trust the Hogg
+Stellar oscillations are stochastically driven high-quality (long-coherence-time) modes.
 If a star is observed through an observing campaign that is shorter
@@
 Here we exploit this to create an inexpensive probabilistic model for
-asteroseismology data.
-The huge advantage of this approach to traditional asteroseismology
+asteroseismology data called \bsa.
+The huge advantage of \bsa\ over to traditional asteroseismology
 approaches is that it does not require the performance of a fourier
@@
 turning the Bayesian crank) without human intervention.
+Much of what is done here could be done with Gaussian Processes; the
+advantages of \bsa\ are that it is conceptually simple, and that it
+has better scaling for some classes of problems.
 \end{abstract}

### 2017-07-02 paper/paper.tex
typo

@@
 asteroseismology data called \bsa.
-The huge advantage of \bsa\ over to traditional asteroseismology
+The huge advantage of \bsa\ over traditional asteroseismology
 approaches is that it does not require the performance of a fourier

### 2017-07-05 paper/paper.tex
Tweak parameter fit and add discussion of likelihood

--- 2017-07-01 paper/paper.tex
@@
 
-\newcommand{\acronym}[1]{{\small{#1}}}
-\newcommand{\project}[1]{\textsl{#1}}
-\newcommand{\kepler}{\project{Kepler}}
-\newcommand{\tess}{\project{\acronym{TESS}}}
-\newcommand{\gaia}{\project{Gaia}}
-\newcommand{\lsst}{\project{\acronym{LSST}}}
+\newcommand{\normal}{\ensuremath{{\rm N}}}
 
-\newcommand{\normal}{\ensuremath{{\rm N}}}
+\newcommand{\prob}{\ensuremath{\rm Pr}}
+\newcommand{\pars}{\ensuremath{\theta}}
+\newcommand{\parsnl}{\ensuremath{\theta_{\rm nl}}}
+\newcommand{\parsl}{\ensuremath{\theta_{\rm lin}}}
+
+\newcommand{\nt}{\ensuremath{n_{t}}}
+\newcommand{\nlin}{\ensuremath{n_{\rm lin}}}
 
@@
 \newcommand{\nuzero}{\ensuremath{\nu_{n00}}}
-\newcommand{\dnu}{\ensuremath{\Delta_\nu}}
+\newcommand{\dnu}{\ensuremath{\Delta\nu}}
 \newcommand{\numax}{\ensuremath{\nu_{\rm max}}}
@@
 \newcommand{\ampc}{\ensuremath{B_{nk\ell}}}
+\newcommand{\eps}{\ensuremath{\kappa_{01}}}
 \newcommand{\rl}{\ensuremath{r_{01}}}
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{TBD}
-\revised{NA}
-\accepted{NA}
+\received{July 1, 2016}
+\revised{September 27, 2016}
+\accepted{\today}
 %% Command to document which AAS Journal the manuscript was submitted to.
@@
 \begin{abstract}
-Stellar oscillations are stochastically driven high-*Q* modes.
-If a star is observed through an observing campaign that is shorter
-than the coherence time of a mode, that mode will effectively appear
-coherent within that time interval.
-Here we exploit this to create an inexpensive probabilistic model for
-asteroseismology data.
-The huge advantage of this approach to traditional asteroseismology
-approaches is that it does not require the performance of a fourier
-transform or anything like it; this permits the measurement of
-asteroseismic parameters in data sets that are irregularly or sparsely
-sampled, or in data sets where the critical modes are near the edges
-of the available frequency space (near the inverse exposure time at
-the high-frequency end or near the inverse of the duration of the
-campaign at the low-freqency end).
-It also permits the construction of a tractable and justifiable
-likelihood function, even when the noise processes are non-trivial.
-We produce a parameterized description of an asteroseismic frequency
-spectrum and use it along with this likelihood function to produce
-posterior estimates of asteroseismic parameters for stars in the
-\kepler\ data.
-We sub-sample the \kepler\ light curves to (short duration)
-\tess-like and (sparsely sampled) \gaia-like data sets and show that
-even in these much smaller data sets, we ought to be able to estimate
-asteroseismic parameters for many stars, and (because we are just
-turning the Bayesian crank) without human intervention.
+
+Things, stuff.
+
 \end{abstract}
@@
 %% keywords and the rules for their use.
-\keywords{editorials, notices --- miscellaneous --- catalogs ---
-  surveys --- methods of limited utility}
+\keywords{editorials, notices --- 
+miscellaneous --- catalogs --- surveys}
 
@@
 asteroseismology with sparse-in-time data, like that which will be
-produced by \lsst\ and \gaia.
+produced by LSST and Gaia.
 
@@
 Finally: Stars are damned coherent. Red giants, in particular, show little
-or no sign of decoherence over the entire duration of the \kepler\ Mission.
+or no sign of decoherence over the entire duration of the Kepler mission.
 That should make life better; how?
@@
 \begin{equation}
-\nukzero = \nuzero (1 + k \dnu), 
+\nukzero = \nuzero \, (1 + k \, \Delta), 
 \end{equation}
@@
 \begin{equation}
-\nukone = \nuzero (1 + (k + 1/2) \dnu), 
+\nukone = \nuzero \, (1 + [k + \eps] \, \Delta), 
 \end{equation}
-Each of these modes corresponds to two sinusoids
+with $\eps \simeq 1/2$. Each of these modes corresponds to two sinusoids
 \begin{equation}
-m(t) = \amps \sin(2\pi\nukl t) + \ampc \cos(2\pi\nukl t)
+m_{k\ell}(t) = \amps \, \sin(2\pi \, \nukl \, t) + \ampc \, \cos(2\pi \, \nukl \, t)
 \end{equation}
-into the stellar lightcurve. The amplitudes, $\{\amps, \ampc\}$, are normally distributed with a frequency- and $\ell$-dependent variance:
+into the stellar lightcurve, yielding $\nlin = 8K+4$ unknown amplitude parameters. The total model lightcurve (i.e., summed over $k$ and $\ell$) can be represented by
 \begin{equation}
-\amps, \ampc \sim \normal \left(\amps, \ampc; 0, \rl^\ell \sigma^2(\nukl) \right),
+m(t) = D(t, \nukl) \, \parsl
+\end{equation}
+where $D$ is an $\nt \, \times \, \nlin$ design matrix and
+\begin{equation}
+\parsl = \{ A_{n,-K,0}, B_{n,-K,0}, A_{n,-K,1}, B_{n,-K,1}, A_{n,-K+1,0}, B_{n,-K+1,0}, \ldots, A_{n,K,1}, B_{n,K,1} \}
+\end{equation}
+is a vector of amplitudes. The amplitudes are Gaussian-distributed with a frequency- and $\ell$-dependent variance; for example, 
+\begin{equation}
+\amps \sim \normal \left(\amps \, ; \, 0, \rl^\ell \, \sigma^2(\nukl) \right),
 \end{equation}
@@
 \begin{equation}
-\sigma^2(\nu) = \numod(\nu; \numax, W, H),
+\sigma^2(\nu) = \numod(\nu \, ; \, \numax, W, H),
 \end{equation}
@@
 \begin{equation}
-\numod(\nu; \numax, W, H) = H \exp \left( -\frac{(\nu - \numax)^2}{2 W^2} \right).
+\numod(\nu \, ; \, \numax, W, H) = H \, \exp \left( -\frac{[\nu - \numax]^2}{2 \, W^2} \right).
+\end{equation}
+This model is therefore completely described by the parameter vector $\pars = \{ \amps, \ampc, \nuzero, \Delta, \eps, \rl, \numax, W, H \}$, depending linearly on the amplitudes, $\parsl = \{\amps, \ampc\}$, and non-linearly on the remainder, $\parsnl$.
+
+In the following, we assume $K=16$, yielding a total of 132 linear parameters and seven non-linear parameters.
+Our aim is to recover the marginal posterior of $\numax$ and $\dnu = \nuzero \, \Delta$, which can be estimated by sampling from the full joint posterior distribution
+\begin{equation}
+\prob(\pars \, | \, d(t)) \propto \prob(\pars) \, \prob(d(t) \, | \, \pars).
+\end{equation}
+Na\"ively this involves the daunting task of sampling from a highly multimodal distribution in 140 dimensions.
+We can, however, greatly reduce the dimensionality by exploiting the linear dependence of the model on the amplitudes.
+Assuming Gaussian noise with time-domain covariance matrix $C$ yields a Gaussian likelihood function
+\begin{equation}
+\prob(d(t) \, | \, \pars) = \normal \left(d(t) \, ; \, m(t, \pars), C \right),
+\end{equation}
+which, coupled with the assumption of Gaussian-distributed amplitudes means we can pre-marginalize over them analytically, yielding
+\begin{eqnarray}
+\prob(d(t) \, | \, \parsnl) & = & \int d\parsl \, \prob(\parsl) \, \prob(d(t) \, | \, \pars) \nonumber \\
+& = & \normal \left(d(t) \, ; \, 0, V(\parsnl) \right).
+\end{eqnarray}
+Here, the modified covariance matrix $V = C + D \, \Lambda \, D^T$, where $\Lambda$ is a diagonal $\nlin^2$ matrix with non-zero entries 
+\begin{equation}
+\parsl = \{ \sigma^2(\nu_{0,-K,0}), \sigma^2(\nu_{0,-K,0}), \sigma^2(\nu_{0,-K,1}), \sigma^2(\nu_{0,-K,1}), \ldots, \sigma^2(\nu_{0,K,1}), \sigma^2(\nu_{0,K,1}) \}.
 \end{equation}
 
-This model is completely described by the parameters $\{ \amps, \ampc, \nuzero, \dnu, \rl, \numax, W, H \}$, depending linearly on the amplitudes, $\{\amps, \ampc\}$, and non-linearly on the remainder.
-In the following, we assume $K=16$, yielding a total of 132 linear parameters and six non-linear parameters.
+The slowest steps in evaluating this likelihood are inverting and finding the determinant of the $\nt^2$ covariance matrix $V$; however, provided $\nlin < \nt$ we can increase the speed of this step (potentially significantly: by a factor of $(\nt/\nlin)^3$) by performing low-rank updates of the data covariance:
+\begin{eqnarray}
+V^{-1} & = & C^{-1} - C^{-1} \, D \, \left(I + \Lambda \, D^T \, C \, D \right)^{-1} \Lambda \, D^T \, C^{-1} \\
+||V|| & = & ||I + \Lambda \, D^T \, C \, D|| \, ||C||.
+\end{eqnarray}
+Using these forms of the two matrix lemmas is important, as the bell function modulating the variances of the linear amplitudes allows for singular $\Lambda$ matrices, particularly when $W$ is small.
 

### 2017-07-05 paper/paper.tex

@@
 
+\newcommand{\acronym}[1]{{\small{#1}}}
+\newcommand{\project}[1]{\textsl{#1}}
+\newcommand{\kepler}{\project{Kepler}}
+\newcommand{\tess}{\project{\acronym{TESS}}}
+\newcommand{\gaia}{\project{Gaia}}
+\newcommand{\lsst}{\project{\acronym{LSST}}}
+\newcommand{\bsa}{\project{\acronym{BSA}}}
+
 \newcommand{\normal}{\ensuremath{{\rm N}}}
@@
 %% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-
-Things, stuff.
-
+\begin{abstract}\noindent % trust the Hogg
+Stellar oscillations are stochastically driven high-quality (long-coherence-time) modes.
+If a star is observed through an observing campaign that is shorter
+than the coherence time of a mode, that mode will effectively appear
+coherent within that time interval.
+Here we exploit this to create an inexpensive probabilistic model for
+asteroseismology data called \bsa.
+The huge advantage of \bsa\ over traditional asteroseismology
+approaches is that it does not require the performance of a fourier
+transform or anything like it; this permits the measurement of
+asteroseismic parameters in data sets that are irregularly or sparsely
+sampled, or in data sets where the critical modes are near the edges
+of the available frequency space (near the inverse exposure time at
+the high-frequency end or near the inverse of the duration of the
+campaign at the low-freqency end).
+It also permits the construction of a tractable and justifiable
+likelihood function, even when the noise processes are non-trivial.
+We produce a parameterized description of an asteroseismic frequency
+spectrum and use it along with this likelihood function to produce
+posterior estimates of asteroseismic parameters for stars in the
+\kepler\ data.
+We sub-sample the \kepler\ light curves to (short duration)
+\tess-like and (sparsely sampled) \gaia-like data sets and show that
+even in these much smaller data sets, we ought to be able to estimate
+asteroseismic parameters for many stars, and (because we are just
+turning the Bayesian crank) without human intervention.
+Much of what is done here could be done with Gaussian Processes; the
+advantages of \bsa\ are that it is conceptually simple, and that it
+has better scaling for some classes of problems.
 \end{abstract}

### 2017-07-06 ana_lightcurves.py
Update code to sample kappa_01: the fractional change in frequency between the ell = 0 and 1 modes. Plot power spectrum and marginalized posteriors of parameters of interest.

@@ -19,8 +19,8 @@ elif ml.model == 'comb':
 # generate parameter labels
 labels = []
 if ml.model == 'star':
-	labels = [r'$\nu_{n00}$', r'$\Delta_\nu$', r'$\nu_{\rm max}$', \
-			  r'$H$', r'$W$', r'$r_{01}$']
+	labels = [r'$\nu_{n00}$', r'$\Delta$', r'$\nu_{\rm max}$', \
+			  r'$H$', r'$W$', r'$r_{01}$', r'$\kappa_{01}$']
 elif ml.model == 'comb' or ml.model == 'comb_marg':
 	labels = [r'$\omega_0$', r'$\Delta\omega$']
 if ml.model == 'ind' or ml.model == 'comb':
@@ -118,4 +118,32 @@ if use_corner:
 										color='red', ls=':', \
 										lw = 1.5)
 	mp.savefig('test_posterior.pdf')
+
+	# produce corner plot for parameters of interest
+	if ml.model == 'star':
+
+		# \Delta_\nu is a derived parameter
+		i_nu_0, i_delta, i_nu_max = (0, 1, 2)
+		s_marg = np.zeros((n_s, 2))
+		s_marg[:, 0] = s[:, i_nu_0] * s[:, i_delta]
+		s_marg[:, 1] = s[:, i_nu_max]
+		p_true_marg = [ p_true[i_nu_0] * p_true[i_delta], \
+						p_true[i_nu_max] ]
+		n_p_marg = len(p_true_marg)
+		labels_marg = [ r'$\Delta_\nu$', r'$\nu_{\rm max}$' ]
+		fig = co.corner(s_marg, bins = 50, labels = labels_marg, \
+						plot_density = False, plot_contours = False, \
+						no_fill_contours = True)
+		for i in range(n_p_marg):
+			for j in range(i):
+				a_ind = i * n_p_marg + j
+				fig.axes[a_ind].axhline(p_true_marg[i], \
+										color='red', ls=':', \
+										lw = 1.5)
+			for j in range(i + 1):
+				a_ind = i * n_p_marg + j
+				fig.axes[a_ind].axvline(p_true_marg[j], \
+										color='red', ls=':', \
+										lw = 1.5)
+		mp.savefig('test_posterior_marg.pdf')
 

### 2017-07-06 fit_lightcurves.py

@@ -58,6 +58,7 @@ def mn_prior_full_comb_marg(cube, n_dim, n_par):
 	cube[4] = ml.log_uniform_prior(cube[4], ml.log_omega_min, \
 								   ml.log_omega_max) / 2.0 / np.pi
 	cube[5] = ml.gaussian_prior(cube[5], 0.5, 0.1)
+	cube[6] = ml.uniform_prior(cube[6], 0.2, 0.8)
 
 # MultiNest log-likelihood
 def mn_log_like(cube, n_dim, n_par):
@@ -102,7 +103,7 @@ def mn_log_like_full_comb_marg(cube, n_dim, n_par):
 	# construct frequencies and their std devs
 	nus, amp_vars = ml.comb_freq_var(ml.k_max, ml.l_max, cube[0], \
 									 cube[1], cube[2], cube[3], \
-									 cube[4], cube[5])
+									 cube[4], cube[5], cube[6])
 	omegas = 2.0 * np.pi * nus
 
 	# calculate log-like
@@ -163,7 +164,7 @@ elif ml.model == 'comb_marg':
 		   n_live_points = 1000, evidence_tolerance = 0.5, \
 		   sampling_efficiency = 0.3)
 elif ml.model == 'star':
-	n_par_fit = 6
+	n_par_fit = 7
 	c_mat = np.diag(np.ones(n_t) * ml.noise_sigma ** 2)
 	c_mat_inv = np.linalg.inv(c_mat)
 	c_mat_log_det = np.linalg.slogdet(2.0 * np.pi * c_mat)[1]
@@ -172,3 +173,4 @@ elif ml.model == 'star':
 		   outputfiles_basename = u'chains/test', \
 		   n_live_points = 1000, evidence_tolerance = 0.5, \
 		   sampling_efficiency = 0.3)
+	

### 2017-07-06 mod_lightcurves.py

@@ -43,19 +43,14 @@ def des_mat(time, omega):
 
 # generate comb of frequencies and their variances
 def comb_freq_var(k_max, l_max, nu_0, d_nu, nu_max, bell_h, bell_w, \
-				  r_01):
+				  r_01, d_k_01 = 0.5):
 
-	# @TODO: QUESTIONS TO ASK
-	# 1 - is the variance at ell=1 half that of the ell=0 mode or 
-	#     half the bell curve at nu_nk1?
-	# 2 - am i drawing the amps from the variances correctly? i don't
-	#     think i should be adjusting by 1/2
 	n_comp = (l_max + 1) * (2 * k_max + 1)
 	ks = np.zeros(n_comp)
 	ind = 0
 	for k in range(-k_max, k_max + 1):
 		for el in range(l_max + 1):
-			ks[ind] = k + el * 0.5
+			ks[ind] = k + el * d_k_01
 			ind += 1
 	els = np.mod(np.arange(n_comp), 2)
 	nus = nu_0 * (1.0 + ks * d_nu)

### 2017-07-06 sim_lightcurves.py

@@ -19,15 +19,34 @@ mp.rcParams['lines.linewidth'] = lw
 t_min = 0.0
 t_max = 30.0 * 24.0 * 60.0 # 30 days in mins
 n_t = int((t_max - t_min) / ml.t_sample)
+constrain = True
 
 # determine accessible frequency range
 nu_min = 1.0 / (t_max - t_min)
 nu_nyq = 0.5 * (n_t - 1) / (t_max - t_min)
 
+# constrain the particular realisation if desired
+if constrain:
+	with open('test_rng_state.txt', 'r') as f:
+		lines = f.readlines()
+	f.closed
+	state = (lines[0].rstrip(), \
+			 np.array(lines[1:-3], dtype = 'uint32'), \
+			 int(lines[-3]), int(lines[-2]), float(lines[-1]))
+	np.random.set_state(state)
+else:
+	state = np.random.get_state()
+	with open('test_rng_state.txt', 'w') as f:
+		f.write(state[0] + '\n')
+		for i in range(len(state[1])):
+			f.write('{:10d}\n'.format(state[1][i]))
+		f.write('{:10d}\n'.format(state[-3]))
+		f.write('{:10d}\n'.format(state[-2]))
+		f.write('{:3.1f}\n'.format(state[-1]))
+	f.closed
+
 # generate signal parameters
 if ml.model == 'star':
-
-	npr.seed(0)
 
 	# number of modes
 	n_comp = (ml.l_max + 1) * (2 * ml.k_max + 1)
@@ -40,11 +59,12 @@ if ml.model == 'star':
 	bell_h = ml.amp_sigma ** 2
 	bell_w = d_nu * nu_0 * 4.0
 	r_01 = 0.5
+	d_k_01 = npr.uniform(0.4, 0.6)
 
 	# construct frequencies and their std devs
 	nus, amp_vars = ml.comb_freq_var(ml.k_max, ml.l_max, nu_0, \
 									 d_nu, nu_max, bell_h, \
-									 bell_w, r_01)
+									 bell_w, r_01, d_k_01)
 	'''for i in range(n_comp):
 		mp.plot([nus[i], nus[i]], [0, amp_sigmas[i] ** 2], 'k')
 	nu_grid = np.linspace(nus[0], nus[-1], 1000)
@@ -106,10 +126,10 @@ with open('test_params.txt', 'w') as f:
[…]
